A geometric framework for capturing high-resolution insights into conceptual knowledge and learning in classroom-like settings

### 2023-01-29 paper/main.tex
move sliding window fig to results section, WIP updates to topic modeling description

@@

Our primary research goal is to advance our understanding of what it means to
acquire deep real-world conceptual knowledge. Traditional laboratory approaches
to studying learning and memory (e.g., list learning studies) often draw little
distinction between memorization and understanding. Instead, these studies
typically focus on whether information is effectively encoded or retrieved,
rather than whether the information is \textit{understood}. Approaches to
studying conceptual learning, such as category learning experiments, can start
to investigate the distinction between memorization and understanding, often by
training participants to distinguish arbitrary or random features in otherwise
meaningless categorized stimuli. However the objective of real-world training,
or learning from life experiences more generally, is often to develop new
knowledge that may be applied in \textit{useful} ways in the future. In this
sense, the gap between modern learning theories and modern pedagogical
approaches and classroom learning strategies is enormous: most of our theories
about \textit{how} people learn are inspired by experimental paradigms and
models that have only peripheral relevance to the kinds of learning that
students and teachers actually seek \citep{Macl05, HallGree08}. To help bridge this gap, our study uses
course materials from real online courses to inform, fit, and test models of
real-world conceptual learning. We also provide a ``proof of concept''
demonstration of how our models might be used to construct ``maps'' of what
students know, and how their knowledge changes with training. In addition to
helping to visualize knowledge (and changes in knowledge), we hope that such
maps might lead to real-world tools for improving how we educate.

@@

At its core, our main modeling approach is based around a simple assumption
that we sought to test empirically: all else being equal, knowledge about a
given concept is predictive of knowledge about similar or related concepts.
From a geometric perspective, this assumption implies that knowledge is
fundamentally ``smooth.'' In other words, as one moves through a space
representing an individual's knowledge (where similar concepts occupy nearby
coordinates), their ``level of knowledge'' should change relatively gradually
throughout that space. To begin to test this smoothness assumption, we sought
to track our participants' knowledge and how it changed over time in response
to training.

@@

We asked participants in our study to answer questions from several multiple-choice
quizzes and watch two lecture videos from the Khan Academy platform
(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
strong and weak interactions, and electromagnetism. The second,
entitled \textit{Birth of Stars}, provided an overview of our current
understanding of how stars form. We selected these lessons to be (a) accessible
to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
(b) conceptually related to each other, i.e., covering at least \textit{some}
similar or overlapping content; and (c) largely independent of each other, i.e., focused
on sufficiently different material that understanding one did not require having seen
the other. Thus, the two videos we selected are introductory, high-level lectures that both 
belong to Khan Academy's ``Cosmology and Astronomy" course domain, but come from
different lecture series (``Scale of the Universe" and ``Stars, Black Holes, and Galaxies" 
for the first and second lectures, respectively).

We also wrote a set of
multiple-choice quiz questions that would enable us to test participants'
knowledge about each individual lecture, as well as related content not
specifically presented in either video ( see Tab.~\questions). Participants answered
questions randomly drawn from each content area (lecture 1, lecture 2, and
general physics knowledge) across each of three quizzes. Quiz 1 was intended to
assessed participants' ``baseline" knowledge before training, quiz 2 assessed knowledge
after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1),
and quiz 3 assessed knowledge after watching the \textit{Birth of Stars} video
(i.e., lecture 2).

@@

Participants reported their undergraduate major(s) as ``social sciences" (28
participants), ``natural sciences" (16 participants), ``professional" (e.g., pre-med or pre-law; 8
participants), ``mathematics and engineering" (7 participants), ``humanities" (4
participants), or ``undecided" (3 participants). Note that some participants
selected multiple categories for their undergraduate major. We also asked
participants about the courses they had taken. In total, 45 participants
reported having taken at least one Khan Academy course in the past, 
and 5 reported not having taken any Khan
Academy courses. Of those who reported having watched at least one
Khan Academy course, 7 participants reported having watched 1--2 courses, 11
reported having watched 3--5 courses, 8 reported having watched 5--10 courses,
and 19 reported having watched 10 or more courses. We also asked participants
about the specific courses they had watched, categorized under different
subject areas. In the ``Mathematics'' area, participants reported having watched
videos on AP Calculus AB (21 participants), Precalculus (17 participants),
Algebra 2 (14 participants), AP Calculus BC (12 participants), Trigonometry (11
participants), Algebra 1 (10 participants), Geometry (8 participants),
Pre-algebra (7 participants), Multivariable Calculus (5 participants),
Differential Equations (5 participants), Statistics and Probability (4
participants), AP Statistics (2 participants), Linear Algebra (2 participants),
Early Math (1 participant), Arithmetic (1 participant), and other videos not
listed in our survey (5 participants). In the ``Science and engineering'' area,
participants reported having watched videos on Chemistry, AP Chemistry, or
Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II (15
participants); Biology, AP Biology; or High school Biology (15 participants);
Health and Medicine (1 participant); or other videos not listed in our survey
(19 participants). We also asked participants whether they had specifically seen the
videos used in our experiment. Of the 45 participants who reported having having
taken at least one Khan Academy course in the past, 44 participants reported that they had not watched the \textit{Four Fundamental Forces} video, and 1 participant reported that they were not sure whether they had watched it. All participants reported that they had not watched the \textit{Birth of Stars} video.
When we asked participants about non-Khan
Academy online courses, they reported having watched or taken courses on
Mathematics (15 participants), Science and engineering (11 participants), Test
preparation (9 participants), Economics and finance (3 participants), Arts and
humanities (2 participants), Computing (2 participants), and other categories
not listed in our survey (18 participants). Finally, we asked participants
about in-person courses they had taken in different subject areas. They
reported taking courses in Mathematics (39 participants), Science and
engineering (38 participants), Arts and humanities (35 participants), Test
preparation (27 participants), Economics and finance (26 participants),
Computing (15 participants), College and careers (7 participants), or other
courses not listed in our survey (6 participants).

\subsection*{Experiment}

We hand-selected two course videos from the Khan Academy platform: \textit{Four
Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
nuclear force, and the strong nuclear force; duration: 10 minutes and 29
seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
duration: 7 minutes and 57 seconds). We hand-wrote 39 multiple-choice
questions: 15 about the conceptual content of \textit{Four Fundamental Forces},
15 about the conceptual content of \textit{Birth of Stars}, and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). The full set of
questions and answer options may be found in Table~\questions.

%Over the course of the experiment, participants completed three multiple-choice quizzes

Participants began the main experiment by answering a battery of 13 randomly
selected questions (chosen from the full set of 39). Then they watched the
\textit{The Four Fundamental Forces} lecture video. Next, they answered a second set of
13 questions (chosen at random from the remaining 26 questions). Fourth,
participants watch the \textit{Birth of Stars} video, and finally they answered
the remaining 13 questions. Our experimental procedure is diagramed in
Figure~\ref{fig:experiment}. We used the experiment to develop and test our
computational framework for estimating knowledge and learning.

@@

We extended an approach developed by~\citep{HeusEtal21} to construct text
embeddings for each moment of each lecture, and of each question in our pool.
Briefly, our approach uses a topic model~\citep{BleiEtal03}, trained on a set
of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
topic is defined as a set of weights over each word in the model's vocabulary
(i.e., the union of all unique words, across all documents, excluding ``stop
words.''). Conceptually, each topic is intended to give larger weights to words
that are conceptually related or that tend to co-occur in the same documents.
After fitting a topic model, each document in the training set, or any
\textit{new} document that contains at least some of the words in the model's
vocabulary, may be represented as a $k$-dimensional vector describing how much
the document (most probably) reflects each topic. (Unless, otherwise noted, we
used $k = 15$ topics.)

\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
Building a document pool from sliding windows of text.} We decompose each
video's transcript into a series of overlapping sliding windows. The set of
transcript snippets (across all windows) may be treated as a set of
``documents'' for training a text embedding model. After training a text
embedding model using the two videos' sliding windows, along with the text from
each question in our pool (Tab.~\questions), } we construct ``trajectories''
through text embedding space by joining the embedding coordinates of successive
sliding windows from each video. \textbf{B. Embedding multiple videos and
questions.} Applying the same text embedding approach to each video, along with
the text of each question, results in one trajectory per video and one
embedding coordinate (dot) per question (blue: \textit{Four Fundamental
Forces}; green: \textit{Birth of Stars}; pink: general physics knowledge). Here
we have projected the 15-dimensional embeddings into a 3D space using Uniform
Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}.}

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy videos are hosted on the YouTube platform, and all
YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
to derive a timestamped transcript of any detected speech in the video. The
resulting transcripts contain one timestamped row per line, and each line
generally corresponds to a few seconds of spoken content from the video. We
defined a sliding window length of (up to) $w = 30$ transcript lines, and we
assigned each window a timestamp according to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This insured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. We treated the text from each sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.

>>>>

\usepackage{xcolor}

@@

Our primary research goal is to advance our understanding of what it means to
acquire deep, real-world conceptual knowledge. Traditional laboratory approaches
to studying learning and memory (e.g., list learning studies) often draw little
distinction between memorization and understanding. Instead, these studies
typically focus on whether information is effectively encoded or retrieved,
rather than whether the information is \textit{understood}. Approaches to
studying conceptual learning, such as category learning experiments, can begin
to investigate the distinction between memorization and understanding, often by
training participants to distinguish arbitrary or random features in otherwise
meaningless categorized stimuli. However the objective of real-world training,
or learning from life experiences more generally, is often to develop new
knowledge that may be applied in \textit{useful} ways in the future. In this
sense, the gap between modern learning theories and modern pedagogical
approaches and classroom learning strategies is enormous: most of our theories
about \textit{how} people learn are inspired by experimental paradigms and
models that have only peripheral relevance to the kinds of learning that
students and teachers actually seek \citep{Macl05, HallGree08}. To help bridge this gap, our study uses
course materials from real online courses to inform, fit, and test models of
real-world conceptual learning. We also provide a
demonstration of how our models can be used to construct ``maps'' of what
students know, and how their knowledge changes with training. In addition to
helping to visualize knowledge (and changes in knowledge), we hope that such
maps might lead to real-world tools for improving how we educate.

@@

At its core, our main modeling approach is based around a simple assumption
that we sought to test empirically: all else being equal, knowledge about a
given concept is predictive of knowledge about similar or related concepts.
From a geometric perspective, this assumption implies that knowledge is
fundamentally ``smooth.'' In other words, as one moves through a space
representing an individual's knowledge (where similar concepts occupy nearby
coordinates), their ``level of knowledge'' should change relatively gradually
throughout that space. To begin to test this smoothness assumption, we sought
to track participants' knowledge and how it changed over time in response
to training.

@@

We asked participants in our study to complete brief multiple-choice quizzes before, between, and after watching two lecture videos from the Khan Academy \citep{Khan04} platform (Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
strong and weak interactions, and electromagnetism. The second,
entitled \textit{Birth of Stars}, provided an overview of our current
understanding of how stars form.
%(See \hyperref[subsec:experiment]{\textit{Experiment}} for more information on how these lectures were chosen.)
%Each multiple-choice quiz consisted of 13 questions that would enable us to test participants'
%knowledge about each individual lecture, as well as related content not
%specifically presented in either video ( see Tab.~\questions).
%
%We selected these lessons to be accessible to a broad audience (i.e., requiring minimal prerequisite knowledge to understand) and largely independent of each other (i.e., focused on sufficiently different material that understanding one did not require having seen the other), but conceptually related to each other (covering at least \textit{some} similar or overlapping content).
We selected these lessons to be (a) accessible
to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
(b) conceptually related to each other, i.e., covering at least \textit{some}
similar or overlapping content; and (c) largely independent of each other, i.e., focused
on sufficiently different material that understanding one did not require having seen
the other. The two videos we selected are introductory lectures that both
belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but are taken from
different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
for the first and second lectures, respectively).

%We asked participants in our study to answer questions from several multiple-choice
%quizzes and watch two lecture videos from the Khan Academy platform
%(Fig.~\ref{fig:experiment}). The first lecture video, entitled \textit{Four
%Fundamental Forces}, discussed the four fundamental forces in physics: gravity,
%strong and weak interactions, and electromagnetism. The second,
%entitled \textit{Birth of Stars}, provided an overview of our current
%understanding of how stars form. We selected these lessons to be (a) accessible
%to a broad audience, i.e., requiring minimal prerequisite knowledge to understand;
%(b) conceptually related to each other, i.e., covering at least \textit{some}
%similar or overlapping content; and (c) largely independent of each other, i.e., focused
%on sufficiently different material that understanding one did not require having seen
%the other. Thus, the two videos we selected are introductory, high-level lectures that both
%belong to Khan Academy's ``Cosmology and Astronomy'' course domain, but come from
%different lecture series (``Scale of the Universe'' and ``Stars, Black Holes, and Galaxies''
%for the first and second lectures, respectively).

We then created a pool of
multiple-choice quiz questions that would enable us to test participants'
knowledge about each individual lecture, as well as related content not
specifically presented in either video ( see Tab.~\questions). Participants answered
questions randomly drawn from each content area (lecture 1, lecture 2, and
general physics knowledge) on each of the three quizzes. Quiz 1 was intended to
assess participants' ``baseline'' knowledge before training, quiz 2 assessed knowledge
after watching the \textit{Four Fundamental Forces} video (i.e., lecture 1),
and quiz 3 assessed knowledge after watching the \textit{Birth of Stars} video
(i.e., lecture 2).

\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
Building a document pool from sliding windows of text.} We decompose each
video's transcript into a series of overlapping sliding windows. The set of
transcript snippets (across all windows) may be treated as a set of
``documents'' for training a text embedding model. After training a text
embedding model on the two videos' sliding windows, we construct ``trajectories''
through text embedding space by joining the embedding coordinates of successive
sliding windows from each video. \textbf{B. Embedding multiple videos and
questions.} Applying the same text embedding approach to each video, along with
the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
embedding coordinate (dot) per question (blue: \textit{Four Fundamental
Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
we have projected the 15-dimensional embeddings into a 3D space using Uniform
Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}

To study how participants' conceptual knowledge changed over the course of the experiment, 
we first sought to characterize the abstract concepts presented to them in each of the two 
lectures. We adapted an approach we developed in prior work \citep{HeusEtal21} to extract 
the latent themes from the lectures' contents using a topic model \citep{BleiEtal03}. Briefly, 
topic models take as input a collection of text documents and learn a set of ``topics'' (i.e., 
latent themes) from their contents. Once fit, a topic model can be used to transform arbitrary 
(potentially new) documents into sets of ``topic proportions,'' describing the weighted blend 
of learned topics reflected in their texts. We parsed automatically generated transcripts of 
the two lectures into overlapping sliding windows, and used these as documents to fit our 
model (Fig.~\ref{fig:sliding-windows}A; see 
\hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures 
and questions}}). The ($k$=15) topics

%To construct a corpus of text documents for the two lectures, we parsed their transcripts into overlapping sliding windows (Fig.~\ref{fig:sliding-windows}A; see \hyperref[subsec:topic-modeling]{\textit{Constructing text embeddings of multiple lectures and questions}})

@@

Participants reported their undergraduate major(s) as ``social sciences'' (28
participants), ``natural sciences'' (16 participants), ``professional'' (e.g., pre-med or pre-law; 8
participants), ``mathematics and engineering'' (7 participants), ``humanities'' (4
participants), or ``undecided'' (3 participants). Note that some participants
selected multiple categories for their undergraduate major. We also asked
participants about the courses they had taken. In total, 45 participants
reported having taken at least one Khan Academy course in the past,
and 5 reported not having taken any Khan
Academy courses. Of those who reported having watched at least one
Khan Academy course, 7 participants reported having watched 1--2 courses, 11
reported having watched 3--5 courses, 8 reported having watched 5--10 courses,
and 19 reported having watched 10 or more courses. We also asked participants
about the specific courses they had watched, categorized under different
subject areas. In the ``Mathematics'' area, participants reported having watched
videos on AP Calculus AB (21 participants), Precalculus (17 participants),
Algebra 2 (14 participants), AP Calculus BC (12 participants), Trigonometry (11
participants), Algebra 1 (10 participants), Geometry (8 participants),
Pre-algebra (7 participants), Multivariable Calculus (5 participants),
Differential Equations (5 participants), Statistics and Probability (4
participants), AP Statistics (2 participants), Linear Algebra (2 participants),
Early Math (1 participant), Arithmetic (1 participant), and other videos not
listed in our survey (5 participants). In the ``Science and engineering'' area,
participants reported having watched videos on Chemistry, AP Chemistry, or
Organic Chemistry (21 participants); Physics, AP Physics I, or AP Physics II (15
participants); Biology, AP Biology; or High school Biology (15 participants);
Health and Medicine (1 participant); or other videos not listed in our survey
(19 participants). We also asked participants whether they had specifically seen the
videos used in our experiment. Of the 45 participants who reported having having
taken at least one Khan Academy course in the past, 44 participants reported that they had not watched the \textit{Four Fundamental Forces} video, and 1 participant reported that they were not sure whether they had watched it. All participants reported that they had not watched the \textit{Birth of Stars} video.
When we asked participants about non-Khan
Academy online courses, they reported having watched or taken courses on
Mathematics (15 participants), Science and engineering (11 participants), Test
preparation (9 participants), Economics and finance (3 participants), Arts and
humanities (2 participants), Computing (2 participants), and other categories
not listed in our survey (18 participants). Finally, we asked participants
about in-person courses they had taken in different subject areas. They
reported taking courses in Mathematics (39 participants), Science and
engineering (38 participants), Arts and humanities (35 participants), Test
preparation (27 participants), Economics and finance (26 participants),
Computing (15 participants), College and careers (7 participants), or other
courses not listed in our survey (6 participants).

\subsection*{Experiment}\label{subsec:experiment}

We hand-selected two course videos from the Khan Academy platform: \textit{Four
Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
nuclear force, and the strong nuclear force; duration: 10 minutes and 29
seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., lecture 1),
15 about the conceptual content of \textit{Birth of Stars} (i.e., lecture 2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). The full set of
questions and answer choices may be found in Table~\questions.

Over the course of the experiment, participants completed three 13-question 
multiple-choice quizzes: the first before viewing lecture 1, the second between 
lectures 1 and 2, and the third after viewing lecture 2 (Fig.~\ref{fig:experiment}). 
The questions appearing on each quiz, for each participant, were randomly 
chosen from the full set of 39, with the constraints that (a) each quiz contain 5
questions about lecture 1, 5 questions about lecture 2, and 3 questions, and 
(b) each question appear exactly once. The order of questions on each quiz,
and the order of answer options for each question, were also randomized. Our
experimental protocol was approved by the Committee for the Protection of 
Human Subjects at Dartmouth College.  We used the experiment to develop 
and test our computational framework for estimating knowledge and learning.

@@

We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
each moment of the two lectures and each question in our pool in a common representational space.
Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03}, 
fit to a corpus of documents to discover a set of $k$ ``topics'' or ``themes'' from their contents.
Formally, each topic is defined as a set of weights over each word in the model's vocabulary
(i.e., the union of all unique words, across all documents, excluding ``stop
words.'').

We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
each moment of the two lectures and each question in our pool in a common representational space.
Briefly, our approach uses a topic model~\citep[Latent Dirichlet Allocation;][]{BleiEtal03}, trained on a set
of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
topic is defined as a set of weights over each word in the model's vocabulary
(i.e., the union of all unique words, across all documents, excluding ``stop
words.''). Conceptually, each topic is intended to give larger weights to words
that are conceptually related or that tend to co-occur in the same documents.
After fitting a topic model, each document in the training set, or any
\textit{new} document that contains at least some of the words in the model's
vocabulary, may be represented as a $k$-dimensional vector describing how much
the document (most probably) reflects each topic. (Unless, otherwise noted, we
used $k = 15$ topics.)

%\begin{figure}[tp]
%\centering
%\includegraphics[width=\textwidth]{figs/sliding_windows}
%
%\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A}.
%Building a document pool from sliding windows of text.} We decompose each
%video's transcript into a series of overlapping sliding windows. The set of
%transcript snippets (across all windows) may be treated as a set of
%``documents'' for training a text embedding model. After training a text
%embedding model on the two videos' sliding windows, we construct ``trajectories''
%through text embedding space by joining the embedding coordinates of successive
%sliding windows from each video. \textbf{B. Embedding multiple videos and
%questions.} Applying the same text embedding approach to each video, along with
%the text of each question in our pool (Tab.~\questions), results in one trajectory per video and one
%embedding coordinate (dot) per question (blue: \textit{Four Fundamental
%Forces}; green: \textit{Birth of Stars}; purple: general physics knowledge). \color{red}{Here
%we have projected the 15-dimensional embeddings into a 3D space using Uniform
%Manifold Approximation and Projection~\citep[UMAP;][]{McInEtal18a}}.}
%
%\label{fig:sliding-windows}
%\end{figure}

As illustrated in Figure~\ref{fig:sliding-windows}A, we first

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy provides professionally created, manual transcriptions of all videos for closed captioning. However, such transcripts would not be readily available in all contexts to which our framework could potentially be applied. Khan Academy videos are hosted on the YouTube platform, which additionally provides automated transcripts

Khan Academy videos are hosted on the YouTube platform, and all
YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
to derive a timestamped transcript of any detected speech in the video. The
resulting transcripts contain one timestamped row per line, and each line
generally corresponds to a few seconds of spoken content from the video. We
defined a sliding window length of (up to) $w = 30$ transcript lines, and we
assigned each window a timestamp according to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This insured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. We treated the text from each sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.
